---
title: "Mentoring Project"
author: "Mark Bi"
date: "26/06/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Note for uncomment all lines with install.packages by deleting the hashtag sign and recomment these lines only need to run on a computer once. 

Choose and import the csv or xlsx file you want to import, assuming that all the dataset being pulled follows this format this rmarkdown file should perform like an actual script. 

Rmarkdown is essentially a script but can add a lot of documentations, it is great for reproducible work/research (Automating). 

First lets import the required packages for data cleaning
```{r}
#install.packages(tidyr)
#install.packages(dplyr)
#install.packages(stringr)
#install.packages("reticulate")
#install.packages("lambda.tools")
#install.packages("xlsx")

library(tidyr)
library(lambda.tools)
library(dplyr)
library(stringr)
library(reticulate)
library(xlsx)
```

```{r}
Data <- read.csv(file.choose())
```

We gotta first change the column names using the first row (Might need to change later) 
```{r}
Data_colnames <- Data[1,]
Data_colnames <- lapply(Data_colnames, as.character)
```

Now we have the entire name done, we can now remove the first two rows, which hinders the process greatly. 
```{r}
colnames(Data) <- Data_colnames
```

```{r}
Data <- Data[-c(1,2),]
```

The goal now is to get only the columns that we want 
```{r}
Matching_Participants <- dplyr::select(Data, `Full Name`, Gender, Email, Phone, Agency, `Work location (suburb) This information will be used in the matching process`, `Length in Public Sector`, Position, `Please give a brief description of the key aspects of your role. (50 words or less)`, `What is your substantive level? - Selected Choice`, `I am applying to be a`, `Why do you want to be a mentor? (max 3 responses)`, `Which of these Public Sector capabilities are your strengths? (max 2 responses)`, `What are your areas of expertise in the Public Sector? - Selected Choice`, `Are you interested in mentoring more than one mentee?`, `Please tell us anything more about yourself, your application or why you want to be a part of the program.`, `I agree to commit to the program for the duration of 8 months and will attend all required meetings/sessions.`, `Why do you want to be a mentee?(max 2 responses)`, `Which specific Public Sector Capabilities would you like to improve (max 2 responses)`, `What Public Sector Experience are you seeking - Selected Choice`, `What Public Sector Experience are you seeking - Other - Text`)
```

The next step is to change the data types from factor into either numeric or character for sanity sake.
```{r}
# Since most columns are character or word type data, therefore start with converting all columns to character is a good start. 
Matching_Participants <-  Matching_Participants %>% mutate_all(as.character)

# The next column to deal with is the substantial level from characters to integers 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L1-2"] <- 1.5 ; 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L3-4"] <- 3.5; 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L5"] <- 5; 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L6"] <- 6 ; 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L7"] <- 7; 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L8"] <- 8 ; 
Matching_Participants$`What is your substantive level? - Selected Choice`[Matching_Participants$`What is your substantive level? - Selected Choice` == "L9 and above"] <- 9

Matching_Participants$`What is your substantive level? - Selected Choice` <- as.numeric(Matching_Participants$`What is your substantive level? - Selected Choice`)

Why_Change <- function(dataset){
  dataset <- gsub("Career advancement", "A", dataset)
  
  dataset <- gsub("Leadership development","B", dataset)
  
  dataset <- gsub("Increase confidence","C", dataset)
  
  dataset <- gsub("Build Networks in the Public Sector", "D", dataset)
  
  dataset <- gsub("Build Networks", "D", dataset)
  
  dataset <- gsub("Learn more about working in the Public Sector","E", dataset)
  
  dataset <- gsub("To share my experience","A", dataset)
  
  dataset <- gsub("To help build Leadership in the Public Sector","B", dataset)
  
  dataset <- gsub("Support others to grow","C", dataset)
  
  dataset <- gsub("Learn from and teach them","E", dataset)
  
  dataset <- gsub("To learn to be an effective mentor","E", dataset)
  
  return(dataset)
}

Matching_Participants$`Why do you want to be a mentor? (max 3 responses)` <-  Why_Change(Matching_Participants$`Why do you want to be a mentor? (max 3 responses)`)

Matching_Participants$`Why do you want to be a mentee?(max 2 responses)` <-  Why_Change(Matching_Participants$`Why do you want to be a mentee?(max 2 responses)`)
```
   Mentee
    Career advancement = A
    Leadership development = B 
    Increase confidence = C
    Build Networks = D
    Learn more about working in the Public Sector = E 
    
   Mentor
    To share my experience = A
    To help build Leadership in the Public Sector = B
    Support others to grow = C
    Build Networks in the Public Sector = D 
    Learn from and teach them = E
    To learn to be an effective mentor = E 

Now that we have a subset of actual using data, we have to flag out those who did not provide the compulsory information, starting with agency, as it doesn't matter if the users applying to be a mentor or mentee, if the user didn't even add that in, gonna need to flag that. 
```{r}
# This dataset will contain all the entries that are deemed not able to be used for matching as these entries are missing mandetory fields. 
Flagged <- (Matching_Participants %>% filter(Agency == "" | `Full Name` == "" | `I am applying to be a` == "" | `What is your substantive level? - Selected Choice` == ""))

# This dataset is a continuation of the previous dataset for consistency sake and these entries/users have the first level of mandetory fields filled in. 

Matching_Participants <- (Matching_Participants %>% filter(Agency != "" & `Full Name` != "" & `I am applying to be a` != "" & `What is your substantive level? - Selected Choice` != ""))
```

Almost forgot, I need to check if there are any duplicates in the dataset 
```{r}
# This subset of data contains multiple entries from the same person based on their names, might follow-up with them 
Matching_Participants_Duplicates <- Matching_Participants[duplicated(Matching_Participants$`Full Name`),]

# This is the subset of the data with the duplicates removed and we will continue to use this dataset for consistency
Matching_Participants <- Matching_Participants[!duplicated(Matching_Participants$`Full Name`),]
```

# Remove all the test cases
```{r}
Matching_Participants <- Matching_Participants[!(str_detect(Matching_Participants$`Full Name`, regex("testing", ignore_case = TRUE))),]
```

Now let's do some checks on Matching_Participants entries that passed the first flagging trial 
```{r}
# Starting off, we can how many of the participants are applying to be mentor and how many are applying to be mentee. 
Num_Mentor <- sum(Matching_Participants$`I am applying to be a` == "Mentor")
Num_Mentee <- sum(Matching_Participants$`I am applying to be a` == "Mentee")
Num_Agency <- length(unique(Matching_Participants$Agency))
Year <- 2019 

sink("Mentoring Program Dataset Details.txt")

# Below are just some statements that I have made to get more insight on the participants
sprintf("There are %s mentors and %f mentees that can be matched", Num_Mentor, Num_Mentee)

if(Num_Mentee > Num_Mentor){
  print("There is more mentees than mentors, therefore it is possible that not all mentee applicants will be accepted")
} else if(Num_Mentee < Num_Mentor){
  print("There is more mentor than mentee, therefore it is possible that not every mentor applicants will be accepted")
}

# This is just some extra information 
Mentor_2_Mentees <- sum(Matching_Participants$`Are you interested in mentoring more than one mentee?` == "Yes")
sprintf("There is about %s mentors willing to take more than one mentee, assuming that two is the max, they can take %f", Mentor_2_Mentees, Mentor_2_Mentees*2)

sprintf("So in total as of current, we can take %s mentees into the program this round", Mentor_2_Mentees*2 + (Num_Mentor- Mentor_2_Mentees))
sprintf("So it seems that there will be about %s mentees that can't be assigned", (Num_Mentee - (Mentor_2_Mentees*2 + (Num_Mentor - Mentor_2_Mentees))))

sink("Mentoring Program Dataset Details.txt", append = TRUE)
sink()
closeAllConnections()
```

In my opinion, the next step is to transform all the answers from question like what are they trying to develope from character/words into numbers for easier classification. 
    
  Which of these Public Sector capabilities are your strengths? (max 2 responses)
    Shape and Manage Strategy - supporting purpose and direction, thinking strategically, harnessing information and opportunities, showing judgement = A
    
    Achieve Results - Identifies and uses resources wisely, applies and builds professional expertise, responds positively to change, take responsibility for managing projects to achieve results = B
    
    Builds Productive Relationships - Nurtures internal and external relationships, Listens to, understands and recognises the needs of others, Values individual differences and diversity, shares learning and supports others = C
    
    Exemplifies Personal Integrity and Self Awareness - Demonstrates public service professionalism and probity, Engages with risk and shows personal courage, Commits to action, Promotes and adopts a positive and balanced approach to work, Demonstrates self awareness and a commitment to personal development. = D
    
    Communicate and Influence Effectively - Communicates clearly, Listens, understands and adaptsto audience, Negotiates confidently. = E
  
  What are your areas of expertise in the Public Sector? (About this section, I still don't have an idea about how am I going to define other)
    Project Management = A
    Policy Advice = B
    Ministerial Communication = C
    Workforce planning/managing employees = D 
    Other (Still trying to figure it out)
    
  Are you interested in mentoring more than one mentee?
    Yes = True 
    No = False 

This is just even more data cleaning to get the dataset fully ready for full classification, something that I want to do is split those answers with a comma separate into two columns that gets first and second preference skills they develop. 
```{r}
# This is separating the skills in terms of their preferences first, second and third, the person don't have to have three preferences, but this just makes my automation part easier 
Matching_Participants <-  Matching_Participants %>% separate(`Why do you want to be a mentor? (max 3 responses)`, sep = ",", c("First preference(Mentor Why)", "Second preference(Mentor Why)", "third preference(Mentor Why)"))
```
# Now we separate the dataset again to get even more first, second and third preferences, this is known as feature engineering. 

# Ok so I got two options to deal with this, either use stringr and regular expression to match and extract. Second option is just simply used a for loop and replace all the answers. 

# Alright lets forget regular expression for now and just focus the answers and categorising them. 

# Lets assign letters to the answers 


This is to deal with those who selected only one 
```{r}
Expertise_change <- function(Dataset){
  Dataset <- gsub("Project Management", "A", Dataset)
  
  Dataset <- gsub("Policy Advice", "B", Dataset)
  
  Dataset <- gsub("Ministerial Communication", "C", Dataset)
  
  Dataset <- gsub("Workforce planning/managing employees", "D", Dataset)
  
  Dataset <- gsub("Other", "E", Dataset)
  
  return(Dataset)
}

Skill_Develope_change <- function(Dataset){
  Dataset <- gsub("Managing Projects", "A", Dataset)
  
  Dataset <- gsub("Policy writing/ advice", "B", Dataset)
  
  Dataset <- gsub("Communicating with Ministers or Senior staff", "C", Dataset)
  
  Dataset <- gsub("Managing others", "D", Dataset)
  
  Dataset <- gsub("Other", "E", Dataset)
  
  return(Dataset)
}

Matching_Participants$`What are your areas of expertise in the Public Sector? - Selected Choice` <-  sapply(Matching_Participants$`What are your areas of expertise in the Public Sector? - Selected Choice`, Expertise_change)

Matching_Participants$`What Public Sector Experience are you seeking - Selected Choice` <- sapply(Matching_Participants$`What Public Sector Experience are you seeking - Selected Choice`, Skill_Develope_change)

Matching_Participants <- Matching_Participants %>% separate(`What Public Sector Experience are you seeking - Selected Choice`, sep = ",", c("Most seeking experience","Second most seeking experience"))
```

```{r}
Answer_Change <- function(Dataset){
  Dataset <- gsub("Shape and Manage Strategy - supporting purpose and direction, thinking strategically, harnessing information and opportunities, showing judgement", "A", Dataset)
  
  Dataset <- gsub("Achieve Results - Identifies and uses resources wisely, applies and builds professional expertise, responds positively to change, takes responsibility for managing projects to achieve results.", "B", Dataset)
  
  Dataset <- gsub("Exemplifies Personal Integrity and Self Awareness - Demonstrates public service professionalism and probity, Engages with risk and shows personal courage, Commits to action, Promotes and adopts a positive and balanced approach to work, Demonstrates self awareness and a commitment to personal development.", "C", Dataset)
  
  Dataset <- gsub("Builds Productive Relationships - Nurtures internal and external relationships, Listens to, understands and recognises the needs of others, Values individual differences and diversity, Shares learning and supports others", "D", Dataset)
  
  Dataset <- gsub("Communicate and Influence Effectively - Communicates clearly, Listens, understands and adapts to audience, Negotiates confidently.", "E", Dataset)
  
  return(Dataset)
}

Matching_Participants$`Which of these Public Sector capabilities are your strengths? (max 2 responses)` <-  sapply(Matching_Participants$`Which of these Public Sector capabilities are your strengths? (max 2 responses)`, Answer_Change)

Matching_Participants$`Which specific Public Sector Capabilities would you like to improve (max 2 responses)` <- sapply(Matching_Participants$`Which specific Public Sector Capabilities would you like to improve (max 2 responses)`, Answer_Change)

Matching_Participants <- Matching_Participants %>% separate(`Why do you want to be a mentee?(max 2 responses)`, sep = ",", c("First Reason to be Mentee", "Second Reason to be Mentee"))
```
This is my first solution to deal with all these text, this part is to deal with those who selected 2 

Now we will setup the boundaries for the mentees
  
  Which specific Public Sector Capabilities would you like to improve (max 2 responses)
        Shape and Manage Strategy - supporting purpose and direction, thinking strategically, harnessing information and opportunities, showing judgement = A
    
    Achieve Results - Identifies and uses resources wisely, applies and builds professional expertise, responds positively to change, take responsibility for managing projects to achieve results = B
    
    Builds Productive Relationships - Nurtures internal and external relationships, Listens to, understands and recognises the needs of others, Values individual differences and diversity, shares learning and supports others = C
    
    Exemplifies Personal Integrity and Self Awareness - Demonstrates public service professionalism and probity, Engages with risk and shows personal courage, Commits to action, Promotes and adopts a positive and balanced approach to work, Demonstrates self awareness and a commitment to personal development. = D
    
    Communicate and Influence Effectively - Communicates clearly, Listens, understands and adaptsto audience, Negotiates confidently. = E
  
  What Public Sector Experience are you seeking
    Managing Projects = 1
    Policy writing/advice = 2 
    Communicating with Ministers or Senior staff = 3 
    Managing others = 4 
    Other (Still haven't figure it how yet)

## This is the part where we will begin to perform some basic matching based on the new columns that we have created, there are two ways to do this, the first one is to use a whole bunch of if-else statements combined with a while loop or for loop. 

## The second option is to use a package, right now most likely, the recommenderlab package(Need more confirmation) or some other package to create a recommender system to recommend a mentee to a mentor and vice versa. Scratch this plan, the recommender system after some research has been deemed not possible at this stage. 

# The problem will be phrased as: 
  # Offering mentors to mentees based on the goals and weaknesses of the mentees and a few other conditions. 
```{r}
# Splitting the dataset even more 
Matching_Participants <- Matching_Participants %>% separate(`Which of these Public Sector capabilities are your strengths? (max 2 responses)`, sep = ",", c("Most capable strength", "Second capable strength"))

Matching_Participants <- Matching_Participants %>% separate(`Which specific Public Sector Capabilities would you like to improve (max 2 responses)`, sep = ",", c("Most want improved skill", "Second most want improved skill"))
```

Starting off, we will match the mentors and mentees based on their department of their substantiative level 

Now we will split the dataset between mentor and mentee for possible comparisons 
```{r}
Mentor <- Matching_Participants[(Matching_Participants$`I am applying to be a` == "Mentor"),]
Mentor <- Mentor[,1:20]

Mentee <- Matching_Participants[(Matching_Participants$`I am applying to be a` == "Mentee"),]
Mentee <- Mentee[,-12:-18]
```

```{r}
Unmatched_Mentee <- nrow(Mentee)
Unmatched_Mentor <- nrow(Mentor)
Level_1_2 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 1.5)
Level_3_4 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 3.5)
Level_1_4 <-  Level_1_2 + Level_3_4
Level_5 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 5)
Level_6 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 6)
Level_7 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 7)
Level_8 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 8)
Level_9 <- Mentee %>% tally(Mentee$`What is your substantive level? - Selected Choice` == 9)
Male <- Matching_Participants %>% tally(Matching_Participants$Gender == "Male")
Female <- Matching_Participants %>% tally(Matching_Participants$Gender == "Female")
```

# Silver Method attempt 2 (Automated, combined silver method to form the gold method)
```{r}
# Add a column 
Mentee$Similarity_Score <- 0
```

# The Gold Method (Would be very complex and I will need more dataset and a list of fully matched past list and its dataset)

Position is not important as is the location. 

So the way to categorise is as followed from most important to least important: 
  Agency can't be the same 
  Mentor level has to be higher than mentee 
  Mentor why is same as mentee why 
  Mentor capability the same as the mentees most desired skill 
  Mentor experience strength is the same as mentee most desired experience 

We will try about 4-5 separate functions that form a chain when working 

First we will get the filtered dataset with the basic requirement fulfilled: Not the same agency and mentor level higher than mentee level. 

We will have a algorithm to automatically for the length of the mentee do a filtered list to do all this for each mentee or mentor. 

Using that we will use the calculating algorithm to calculate the similarity score iteratively and order the dataset in descending order and match that mentor with the first mentee. 

Lastly using that algorithm of deleting rows, we will delete the rows of matched pairs and keep doing this until one dataset is empty (Done with while loop best) 

```{r}
Data_Filtering <- function(Mentor, Mentee, People){
  Mentor_Agency <- Mentor[People,5]
  Mentor_Level <- Mentor[People,10]
  Filtered <- (Mentee %>% filter(Agency != Mentor_Agency &`What is your substantive level? - Selected Choice` < Mentor_Level))
  
  return(Filtered)
}
```

```{r}
Mentee_Delete <- function(Mentee, Mentee.name){
  Mentee <- Mentee[!(Mentee$`Full Name` == Mentee.name),]
  
  return(Mentee)
}

Mentor_Delete <- function(Mentor, Mentor.name){
  Mentor <- Mentor[!(Mentor$`Full Name` == Mentor.name),]
  
  return(Mentor)
}
```
# Some more outputs of csv files for the report 
```{r}
# First lets get like the number of mentors vs the number of mentees 
Mentor_vs_Mentee <- cbind(Num_Mentor, Num_Mentee)
write.csv(Mentor_vs_Mentee, "Mentor vs Mentee.csv")
# The next step is to get the different departments counts 
Mentor_Agency <- Mentor %>% group_by(Agency) %>% tally()
write.csv(Mentor_Agency, "Mentor Agency.csv")
Mentee_Agency <- Mentee %>% group_by(Agency) %>% tally()
write.csv(Mentee_Agency, "Mentee Agency.csv")
# Then we will get the data for the levels of mentor and mentees 
Mentor_Level <- Mentor %>% count(`What is your substantive level? - Selected Choice`)
write.csv(Mentor_Level, "Mentor Level.csv")
Mentee_Level <- Mentee %>% count(`What is your substantive level? - Selected Choice`)
write.csv(Mentee_Level, "Mentee Level.csv")
```

```{r}
Similarity_Score_Calculation <- function(Loop_Data, Mentor, Mentee, People){
  Mentor_Name <- Mentor[People,1]
  Mentor_Agency <- Mentor[People,5]
  Mentor_Level <- Mentor[People,10]
  Mentor_First_Preference <- Mentor[People,12]
  Mentor_Second_Preference <- Mentor[People,13]
  Mentor_Strength <- Mentor[People,15]
  Mentor_Second_Strength <- Mentor[People,16]
  Mentor_Expertise <- Mentor[People,17]
  
  for(i in 1:nrow(Loop_Data)){
  if(is.na(Loop_Data[i,14]) | is.na(Mentor_First_Preference)){
    next
  } else{
    if(Loop_Data[i,14] == Mentor_First_Preference){
      Loop_Data$Similarity_Score[i] = Loop_Data$Similarity_Score[i] + 1
    }
  }
  }
  
  for(i in 1:nrow(Loop_Data)){
  if(is.na(Loop_Data[i,15])| is.na(Mentor_Second_Preference)){
    next
  } else{
    if(Loop_Data[i,15] == Mentor_Second_Preference){
      Loop_Data$Similarity_Score[i] = Loop_Data$Similarity_Score[i] + 1
    }
  }
  }
  
  for(i in 1:nrow(Loop_Data)){
  if(is.na(Loop_Data[i,16])| is.na(Mentor_Strength)){
    next
  } else{
    if(Loop_Data[i,16] == Mentor_Strength){
      Loop_Data$Similarity_Score[i] = Loop_Data$Similarity_Score[i] + 1
    }
  }
  }
  
  for(i in 1:nrow(Loop_Data)){
  if(is.na(Loop_Data[i,17])| is.na(Mentor_Second_Strength)){
    next
  } else{
    if(Loop_Data[i,17] == Mentor_Second_Strength){
      Loop_Data$Similarity_Score[i] = Loop_Data$Similarity_Score[i] + 1
    }
  }
  }
  
  for(i in 1:nrow(Loop_Data)){
  if(is.na(Loop_Data[i,18]) | is.na(Mentor_Expertise)){
    next
  } else{
    if(Loop_Data[i,18] == Mentor_Expertise){
      Loop_Data$Similarity_Score[i] = Loop_Data$Similarity_Score[i] + 1
    }
  }
  }
  
  Loop_Data[order(Loop_Data$Similarity_Score, decreasing = TRUE),]
  return(Loop_Data)
}
```

```{r}
Mentor_Matched <- data.frame(matrix(ncol=0,nrow=0))
Mentee_Matched <- data.frame(matrix(ncol=0,nrow=0))
```

```{r}
while(nrow(Mentor) != 0 | nrow(Mentee) != 0){
for(i in 1:nrow(Mentor)){
  A = Data_Filtering(Mentor, Mentee, People = i)
  if(nrow(A) == 0){
    next
  } else{
    if(nrow(A) != 0){
      B = Similarity_Score_Calculation(A, Mentor, Mentee, i)
      B = B[order(B$Similarity_Score, decreasing = TRUE),]
      Mentee_Name = B$`Full Name`[1]
      MentorName =  Mentor$`Full Name`[i]
      Mentor_Matched <- rbind(Mentor_Matched, Mentor[i,])
      Mentee_Matched <- rbind(Mentee_Matched, B[1,])
      Mentor <- Mentor_Delete(Mentor, Mentor.name = MentorName)
      Mentee <- Mentee_Delete(Mentee, Mentee.name = Mentee_Name)
    }
  }
}
}
```

```{r}
# Please run this chunk to get the excel csv of the matched pairs. 
Matched_Mentee_Name <- Mentee_Matched$`Full Name`
Matched_Mentor_Name <- Mentor_Matched$`Full Name`
Matched_Mentee_Level <- Mentee_Matched$`What is your substantive level? - Selected Choice`
Matched_Mentor_Level <- Mentor_Matched$`What is your substantive level? - Selected Choice`
Matched_Mentee_Agency <- Mentee_Matched$Agency
Matched_Mentor_Agency <- Mentor_Matched$Agency
Matched_Mentee_Position <- Mentee_Matched$Position
Matched_Mentor_Position <- Mentor_Matched$Position

Matched_Dataset <- cbind(Matched_Mentee_Name, Matched_Mentor_Name, Matched_Mentee_Level, Matched_Mentor_Level, Matched_Mentee_Agency, Matched_Mentor_Agency, Matched_Mentee_Position, Matched_Mentor_Position )
write.csv(Matched_Dataset, "Matched_Pairs.csv")
```

```{r}
Mentee_Mentor_Gender <- table(Matching_Participants$Gender, Matching_Participants$`I am applying to be a`)
write.csv(Mentee_Mentor_Gender, "Gender Ratio.csv")

# Matched vs unmatched mentees 
Mentee_Matches <- nrow(Mentee_Matched)
Mentee_UnMatched <- nrow(Mentee)
Matched_vs_unMatched <- cbind(Mentee_Matches, Mentee_UnMatched)
write.csv(Matched_vs_unMatched, "Matched vs Unmatched.csv")

# Gender Ratio based on agency 
Gender_And_Ratio <- table(Matching_Participants$Gender, Matching_Participants$Agency)
write.csv(Gender_And_Ratio, "Gender and Agency.csv")

# Level and Agency 
Level_And_Agency <- table(Matching_Participants$Agency, Matching_Participants$`What is your substantive level? - Selected Choice`)
write.csv(Level_And_Agency, "Level and Agency.csv")
```

```{r}
write.xlsx(Matched_Dataset, file = "Mentor-Mentee.xlsx", sheetName = "Matched Pairs", append = TRUE)

if(nrow(Mentor) == 0){
  write.xlsx(Mentee, file = "Mentor-Mentee.xlsx", sheetName = "Unmatched Mentees", append = TRUE)
} else if(nrow(Mentee) == 0){
  write.xlsx(Mentor, file = "Mentor-Mentee.xlsx", sheetName = "Unmatched Mentors", append = TRUE)
}

Stats <- cbind(Year, Num_Mentor, Num_Mentee, Num_Agency, Unmatched_Mentor, Unmatched_Mentee, Level_1_2, Level_3_4, Level_5, Level_6, Level_7, Level_8, Level_9, Male, Female)
colnames(Stats) <- c("Year","Mentors","Mentees","Agencies","Unmatched Mentors","Unmatched Mentees","Level 1-2","Level 3-4", "Level 5","Level 6","Level 7","Level 8", "Level 9 or above","Male","Female")
write.xlsx(Stats, file = "Mentor-Mentee.xlsx", sheetName = "Stats", append = TRUE)
```

```{r}
# The function (Silver Goal)
# Use this function if you want to do semi-manual matching 
Mentee_Selection <- function(Mentee, Mentor, row.number){
  Mentor_Name <- Mentor[row.number,1]
  Mentor_Agency <- Mentor[row.number,5]
  Mentor_Level <- Mentor[row.number,10]
  Mentor_First_Preference <- Mentor[row.number,12]
  Mentor_Second_Preference <- Mentor[row.number,13]
  Mentor_Strength <- Mentor[row.number,15]
  Mentor_Second_Strength <- Mentor[row.number,16]
  Mentor_Expertise <- Mentor[row.number,17]
  
  # The must requirement 
  Filtered <- (Mentee %>% filter(Agency != Mentor_Agency &`What is your substantive level? - Selected Choice` < Mentor_Level ))
  
  # Skill Filter 
  Skill_Filter <- (Filtered %>% filter(Mentor_First_Preference == `First Reason to be Mentee` | Mentor_Second_Preference == `Second Reason to be Mentee` & Mentor_Strength == `Most want improved skill` | Mentor_Second_Strength == `Second most want improved skill` & Mentor_Expertise == `Most seeking experience`))
  
  write.csv(Mentor[row.number,], paste0(Mentor_Name,"_detail.csv"))
  
  if(is.empty(Skill_Filter) == TRUE){
    write.csv(Filtered, paste0(Mentor_Name,"_Mentees.csv"))
  } else if (is.empty(Skill_Filter) == FALSE){
    write.csv(Skill_Filter, paste0(Mentor_Name,"_Mentees.csv"))
  }
}

#Mentee_Selection(Mentee,Mentor,1)
```

```{r}
# Final step of semi-automated process
# Type in the name of the mentee and mentor name in and run this section of code. 
Mentor_Delete(Mentor, Mentor.name = "")
Mentee_Delete(Mentee, Mentee.name = "")
```

